\sysfull

### 2018-08-04 paper/asplos19/intro.tex
intro modified

\noindent\textbf{Drawback of Static Task Decomposition.} 
Task-based programming and execution models require a
programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of tasks.  A \emph{task}, a top level function, can
include arbitrary computation that should be executed despite arbitrarily-timed power failures.
The programmer (or a compiler) explicitly expresses task-to-task control flow.
Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and
shows how tasks transitions can impose a run-time overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at run-time.
%
A programmer may thus create very large tasks in an attempt to reduce task transitions
overhead. However, a very large task may require more energy to complete than a device's fixed hardware energy
buffer can hold which may lead to a task \emph{non-termination} problem. To eliminate this risk,
existing systems require the programmer to decompose a program into relatively small tasks to preserve execution progress. These constraints on task sizing leave an unsatisfying dilemma: large, efficient tasks that risk non-termination, or small tasks that are guaranteed to complete, but incur a high task transition and commit overhead. In this work,
we propose a third way, using a novel technique called \emph{adaptive task size execution by task coalescing/splitting} that efficiently executes small tasks, trimming unnecessary overheads, while avoiding the risk of non-termination.
%

@@

%\begin{itemize}
%\item\textit{challenge} 1) Given unpredictable energy shots arrival, how to specify the size of a dynamic task on the fly? \textit{contribution---1} \sys addresses this challenge by using its \textit{recent execution history} as a metric to estimate the environment energy conditions. Furthermore, It mitigates the risk of dynamic task re-execution by taking advantage of the certainty that the energy buffer offers and approaches the expected power interrupt carefully. 
%%
%\item\textit{challenge} 2) Given dynamic variables dependencies, how to ensure efficient data protection against power interrupts? \textit{contribution---2} \sys ensures the consistency of the data by using a novel
%approach called \emph{dynamic group privatization}. Varying variables dependencies forces a static approach (i.e.~\cite{alpaca}) to operate by considering a worst case scenario (i.e. protecting all global variables) in each dynamic task transition. \sys, therefore, utilizes a real-time data tracking to enable partial data protection on a task transition. Individual variables tacking, however, slows down a system dramatically. Therefore, \sys  relies on a coarse locality principle and protects the global variables in a batch. Moreover, it optimizes the data transfer by using Direct Memory Access (DMA).
%%
%\item\textit{challenge} 3) A static task decomposition model assumes that each
%single task can execute to completion. If the hardware energy buffer provides
%inadequate energy to execute each single task to completion, a program will not
%terminate~\cite{cleancut_2018}. under such conditions how to enable the dynamic execution model to progress on a sub-task level? \textit{contribution---3} To avoid non-termination under adversarial
%energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
%Partial execution avoids non-termination by committing the intermediate state of a long-running
%task that has repeatedly failed and restarted. Partial execution violates
%task atomicity, but preserves forward progress; if a programmer knows that
%task atomicity is crucial to correctness, they can disable partial execution around a piece of code.
%\end{itemize}
%
The rest of this paper is organized as follows. Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while
Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism. Dynamic group privatization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
context of related work and Section~\ref{sec:conclusions} concludes and discusses
future work.

>>>>

\noindent\textbf{Crucial Drawback of Static Task Decomposition.} 
Task-based programming and execution models require a
programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of tasks.  A \emph{task}, a top level function, can
include arbitrary computation that should be executed despite arbitrarily-timed power failures.
The programmer (or a compiler) explicitly expresses task-to-task control flow.
Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and
shows how tasks transitions can impose a run-time overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at run-time.
%
A programmer may thus create very large tasks in an attempt to reduce task transitions
overhead. However, a very large task may require more energy to complete than a device's fixed hardware energy
buffer can hold which may lead to a task \emph{non-termination} problem. To eliminate this risk,
existing systems require the programmer to decompose a program into relatively small tasks to preserve execution progress. These constraints on task sizing leave an unsatisfying dilemma: large, efficient tasks that risk non-termination, or small tasks that are guaranteed to complete, but incur a high task transition and commit overhead. In this work,
we propose a third way, using a novel technique called \emph{adaptive task size execution by task coalescing/splitting} that efficiently executes small tasks, trimming unnecessary overheads, while avoiding the risk of non-termination.
%

@@

%\begin{itemize}
%\item\textit{challenge} 1) Given unpredictable energy shots arrival, how to specify the size of a dynamic task on the fly? \textit{contribution---1} \sys addresses this challenge by using its \textit{recent execution history} as a metric to estimate the environment energy conditions. Furthermore, It mitigates the risk of dynamic task re-execution by taking advantage of the certainty that the energy buffer offers and approaches the expected power interrupt carefully. 
%%
%\item\textit{challenge} 2) Given dynamic variables dependencies, how to ensure efficient data protection against power interrupts? \textit{contribution---2} \sys ensures the consistency of the data by using a novel
%approach called \emph{dynamic group privatization}. Varying variables dependencies forces a static approach (i.e.~\cite{alpaca}) to operate by considering a worst case scenario (i.e. protecting all global variables) in each dynamic task transition. \sys, therefore, utilizes a real-time data tracking to enable partial data protection on a task transition. Individual variables tacking, however, slows down a system dramatically. Therefore, \sys  relies on a coarse locality principle and protects the global variables in a batch. Moreover, it optimizes the data transfer by using Direct Memory Access (DMA).
%%
%\item\textit{challenge} 3) A static task decomposition model assumes that each
%single task can execute to completion. If the hardware energy buffer provides
%inadequate energy to execute each single task to completion, a program will not
%terminate~\cite{cleancut_2018}. under such conditions how to enable the dynamic execution model to progress on a sub-task level? \textit{contribution---3} To avoid non-termination under adversarial
%energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
%Partial execution avoids non-termination by committing the intermediate state of a long-running
%task that has repeatedly failed and restarted. Partial execution violates
%task atomicity, but preserves forward progress; if a programmer knows that
%task atomicity is crucial to correctness, they can disable partial execution around a piece of code.
%\end{itemize}
%

The rest of this paper is organized as follows. Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while
Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism. Dynamic group privatization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
context of related work and Section~\ref{sec:conclusions} concludes and discusses
future work.
